\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-16 manuscript/manuscript.tex
updated

We expect this model to have a high consistency of difference between revenue and the \emph{perfect foresight strategy}, with higher revenue than the baseline model and potential room for improvement.

\subsection{Adaptive Likelihood Price Policy}
The fourth policy we will investigate is an adaptive likelihood price method. 
This method is similar to the naïve adaptive likelihood policy with a critical difference. 
Instead of using the estimated unit price increase this model aggregates the revenue from 10 separate forecasts for the remaining weeks. 
The 10 forecasts are run for each price point remaining and are based on randomly selected observed data from pervious runs.  
The model should help capture the original model’s randomness through more robust forecasts.

@@

\subsection{Reinforcement Learning}
A proposed final future state policy is the reinforcement learning strategy. 
Artificial intelligence models rely on supervised reinforcement learning which learn as they go. 
The models are rewarded for certain actions and attempt to maximize the reward, relying on previous runs or iterations to build off of. 
These models are ideal for repeated tasks that have defined conditions. For example, Open Ai in 2019 demonstrated a reinforcement learning model that simulated a game of hide and seek \cite{baker2019emergent}. 
We will apply reinforcement learning to this problem, where the reward function is the maximization of the revenue, and the inputs are from the app itself. 
While this model offers little explanation ability since rl models are black box models, the reinforcement learning policy may perform better than previous policies.

@@

\subsection{Data Treatment}
While we have access to 15 runs of “historical” data, before using this data, we must apply data preprocessing.
\pagebreak

@@

\subsection{Simulation}
To forecast the impact of the pricing strategies we are investigating, we must test the policies against data. 
Since we cannot access the exact equation or similar random number generator used for the web app, we must first utilize simulations. 
The model built takes the policy, the average and the standard deviation of the observed price points and generates 100 simulations. 
For each simulation and each time t, the model generates unit sales based on a numpy random normal method using the mean and standard deviation of the current price point. 
The simulation approach best reflects a real-life scenario as a forecast function is generally unknown, resulting in a reliance on past data to predict future demand. 
The generated numbers reflect the data distribution found within the historical data.
\pagebreak

@@

\subsection{Validation}
The simulation approach helps validate the models and quickly select the best policy with limited information. 
However, for this context, we need not rely solely on the simulation data, we can instead use the actual data from the web app. 
The assumptions and approach we have previously laid out may have unknown challenges or other pitfalls. 
In this scenario we are not limited to the simulation and approximation of “real world data”. 
We will therefore validate the simulation results using the web application. 
To implement the validation, we will utilize a selenium-based python script which goes between the code and user interface on the web app. 
Each policy is tested in real-time against the app while recording the results to evaluate after the fact. \\

@@

Figure 5 demonstrates the relationship between prices and sales in different policies. 
Policies with better performance such as Naïve Adaptive Likelihood, Likelihood Demand Trend Projection, and Moving Average Naïve, share a common characteristic: adopting price change steadily. 
These models take more time waiting and observing the market before adjusting prices accordingly. 
Conversely, Long Term Adaptive Moving Average and Adaptive likelihood price policy tend to lower the price immediately once the product is not in great demand. 
These policies often drop prices around week 6 to week 8 and significantly increase sales afterward. 
Yet, with discounted prices, the average revenue does not outperform others. 
Figure 6 demonstrates the weekly sales figures for each model and validates this observation. 
For instance, the average long-term policy drops the price around 8 weeks for an immediate sales increase, but quickly panics and keeps lowering the price until the 40\% discount is reached. 
The models with a slower price markdown strategy perform best in total revenue generation.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{pic/f3.png}
    \caption{Naïve Adaptative Likelihood Policy Decision Tree}
\end{figure}

\hfill \break
\indent We expect this model to have a high consistency of difference between revenue and the \emph{perfect foresight strategy}, with higher revenue than the baseline model and potential room for improvement.

\subsection{Adaptive Likelihood Price Policy}
The fourth policy is an adaptive likelihood price method. 
This method is similar to the naïve adaptive likelihood policy with a critical difference. 
Instead of using the estimated unit price increase this model aggregates the revenue from 10 separate forecasts for the remaining weeks. 
In other words, the model computes the expected revenue for 10 separate “what if” forecasts based on the observed distributions of historic data and assumes the price will not change before week 15.  
The revenue from the 10 forecasts run for each price point remaining at time t are summed and the one with the largest total revenue is used as the new price point. 
The model should help capture the original model’s randomness through more robust forecasts.

@@

\subsection{Reinforcement Learning}
A proposed final future state policy is the reinforcement learning strategy. 
Artificial intelligence models rely on supervised reinforcement learning which learn as they go. 
The models are rewarded for certain actions and attempt to maximize the reward, relying on previous runs or iterations to build off of. 
These models are ideal for repeated tasks that have defined conditions. For example, Open AI in 2019 demonstrated a reinforcement learning model that simulated a game of hide and seek \cite{baker2019emergent}. 
We will apply reinforcement learning to this problem, where the reward function is the maximization of the revenue, and the inputs are from the app itself. 
While this model offers little explanation ability since reinforcement learning models are black box models, the reinforcement learning policy may perform better than previous policies.

@@

\subsection{Data Treatment}
While we have access to 15 runs of “historical” data, before using this data, we must apply data preprocessing.

@@

\subsection{Simulation}
To forecast the impact of the pricing strategies we are investigating, we must test the policies against data. 
Since we cannot access the exact equation or similar random number generator used for the web app, we must first utilize simulations. 
The model built takes the policy, the average and the standard deviation of the observed price points and generates 100 simulations. 
For each simulation and each time t, the model generates unit sales based on a numpy random normal method using the mean and standard deviation of the current price point. 
The simulation approach best reflects a real-life scenario as a forecast function is generally unknown, resulting in a reliance on past data to predict future demand. 
The generated numbers reflect the data distribution found within the historical data.\\

@@

\subsection{Validation}
The simulation approach helps validate the models and quickly select the best policy with limited information. 
However, for this context, we need not rely solely on the simulation data, we can instead use the actual data from the web app. 
The assumptions and approach we have previously laid out may have unknown challenges or other pitfalls. 
In this scenario we are not limited to the simulation and approximation of “real world data”. 
We will therefore validate the simulation results using the web application. 
To implement the validation, we will utilize a selenium-based python script which goes between the code and user interface on the web app. 
Each policy is tested in real-time against the app while recording the results to evaluate after the fact.

@@

Figure 5 demonstrates the relationship between prices and sales in different policies. 
Policies with better performance such as Naïve Adaptive Likelihood, Likelihood Demand Trend Projection, and Moving Average Naïve, share a common characteristic: adopting price change steadily. 
These models take more time waiting and observing the market before adjusting prices accordingly. 
Conversely, Long Term Adaptive Moving Average and Adaptive likelihood price policy tend to lower the price immediately once the product is not in great demand. 
These policies often drop prices around week 6 to week 8 and significantly increase sales afterward. 
Yet, with discounted prices, the average revenue does not outperform others. 
Figure 6 demonstrates the weekly sales figures for each model and validates this observation. 
For instance, the average long-term policy drops the price around 8 week for an immediate sales increase, but quickly panics and keeps lowering the price until the 40\% discount is reached. 
The models with a slower price markdown strategy perform best in total revenue generation.
